### 2013-11-12 inst/doc/manuscript.Rmd
nexml_read always reads in nexml format now

@@

@@

The `RNeXML` package is built for the NeXML Schema, [version 2009], using the R software environment and the XML package for parsing and generating XML [Temple Lang 2013, XML].

@@

The `RNeXML` package can performs two levels of validation on NeXML files written from or read into R: validating the XML, and validating against the current NeXML schema.

>>>>

Using the nexml and nexmlTree class for metadata.

@@

Temporal, spatial, taxonomic coverage for dryad/knb?

@@

The `RNeXML` package is built for the NeXML Schema, [version 2009], using the R software environment and the XML package for parsing and generating XML [Temple Lang 2013, XML], and provides conversions into the popular `phylo` format provided by the `ape` package [Paradis 2004].  `RNeXML` can automatically check taxonomic names and add taxonomic identifiers when generating NeXML using methods from the `taxize` package ([Chamberlain 2013]).

@@

The `RNeXML` package performs two levels of validation on NeXML files written from or read into R: validating the XML, and validating against the current NeXML schema.
